---
title: "p8105_hw3_js5962"
author: "Jiayao Sun"
date: '2021-10-18'
output: github_document
---

```{r 0, include = FALSE, warning = FALSE}
library(tidyverse)
library(ggridges)
library(readxl)
library(p8105.datasets)
```


**Problem 1**

a) How many aisles are there, and which aisles are the most items ordered from?
```{r 1a}
data("instacart")

# How many aisles are there, and which aisles are the most items ordered from?
instacart %>%
  count(aisle) %>%
  arrange(desc(n))
```

_Comment:_ 134 aisles in total.

b) Then, make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.


```{r 1b}

instacart %>% 
	count(aisle) %>% 
	filter(n > 10000) %>% 
	mutate(
		aisle = factor(aisle),
		aisle = fct_reorder(aisle, n)
	) %>% 
	ggplot(aes(x = aisle, y = n)) + 
	geom_point() + 
	theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "Number of items ordered per aisle",
    x = "Aisle",
    y = "Number of items",
    caption = "limit aisles with more than 10,000 items ordered")
```

_Comment:_ Among aisles with more than 10,000 items ordered, top three ordered aisles are Fresh vegetables, Fresh fruits, and packaged vegetables and fruits; butter has smallest number of items ordered.

c) Next, make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r 1c}
instacart %>% 
	filter(
	  aisle %in% 
	    c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
	group_by(aisle) %>% 
	count(product_name) %>% 
	mutate(rank = min_rank(desc(n))) %>% 
	filter(rank <= 3) %>% 
	arrange(aisle, rank) %>% 
	knitr::kable()
```

_Comment:_ n represents for the number of product ordered. Rank means the rank of products in its aisles. We can find that suger and soda are most popular in baking ingredients. Dog food care sells most in chicken & rice recipe. Packaged vagetables fruits sells most in organic foods, especially organic baby spinach.

d) Next, make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r 1d, message = FALSE, warning = FALSE}
instacart %>% 
	filter(
	  product_name %in% 
	    c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>%  # the day of the week on which the order was placed
  summarize(mean_hour = mean(order_hour_of_day)) %>% # the hour of the day on which the order was placed
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	) %>%
  rename(Sunday = "0", Monday = "1", Tuesday = "2", Wednesday = "3", Thursday = "4", Friday = "5", Saturday = "6") %>% 
  knitr::kable()
```

_Comment:_ Compared to sale in weekend and friday, coffee ice cream sales more on Monday to Thursay. Pink lady apples sale most in Wednesday and least in Monday.

***A short description of the data set***

The data instacart is a clean and imited version of he original data collected from online grocery instarcart. The dataset contains `r count(instacart)` observations of 131,209 unique users, where each row in the dataset is a product from an order. 
There is a single order per user in this dataset.

There are 15 variables in this dataset, following are the key variables:

order_id: order identifier

product_id: product identifier

reordered: 1 if this prodcut has been ordered by this user in the past, 0 otherwise

order_dow: the day of the week on which the order was placed

order_hour_of_day: the hour of the day on which the order was placed

days_since_prior_order: days since the last order, capped at 30, NA if order_number=1

product_name: name of the product

aisle_id: aisle identifier

department_id: department identifier

Through observation above, we know that there are 134 aisles in total, in which aisle fresh vegetables has most orders and fresh fruit the second, which shows that customers use instacart more on fresh and uncooked food. We could advance the marketing on those popular aisles and give coupons of low sale products in case of piling stocks. Meanwhile, we could find out the popular products in each aisle and explore whether ther exists pattern on those products, such as analyzing the order fluctuation according to day of the week.

**Problem 2**

```{r start}
data("brfss_smart2010")
```

First, do data cleaning

```{r data_clean, warning = FALSE}
brfss_df = 
  janitor::clean_names(brfss_smart2010) %>%
  filter(topic == "Overall Health") %>%
  filter(response == "Excellent" | response == "Very good" | response == "Good" | response == "Fair" | response == "Poor") %>%
  mutate(respone = as.factor(response),
  response = forcats::fct_relevel(response, c("Poor", "Fair", "Good", "Very good", "Excellent")))
```

a) In 2002, which states were observed at 7 or more locations? What about in 2010?

```{r 2a}
# in 2002
brfss_df %>%
  filter(year == "2002") %>%
  group_by(locationabbr) %>%
  distinct(locationdesc) %>%
  summarize(numbers_of_tested_locations = n()) %>%
  filter(numbers_of_tested_locations > 6) %>%
  arrange(numbers_of_tested_locations) %>%
  knitr::kable(caption = "Note: states observed at 7 or more location in 2002 as above.")

# in 2010
brfss_df %>%
  filter(year == "2010") %>%
  group_by(locationabbr) %>%
  distinct(locationdesc) %>%
  summarize(numbers_of_tested_locations = n()) %>%
  filter(numbers_of_tested_locations > 6) %>%
  arrange(numbers_of_tested_locations) %>%
  knitr::kable(caption = "Note: states observed at 7 or more location in 2010 as above.")
```

_Comment:_ 6 states were observed at 7 or more locations in 2002. 14 states were observed at 7 or more locations in 2010, which is larger compared to 2002.

b) Next, construct a data set that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r 2b}
brfss_excellent =
  brfss_df %>%
  filter(response == "Excellent") %>%
  group_by(year, locationabbr) %>%
  mutate(average_data_value = mean(data_value, na.rm = TRUE))
# create plots
brfss_excellent %>%
ggplot(aes(x = year, y = average_data_value, group = locationabbr, color = locationabbr)) + 
  geom_line() +
  geom_point(alpha = 0.3) +
  labs(
    title = "Average data value of each state in 2002-2010",
    x = "Year",
    y = "Average data value", 
    caption = "Note: Data from brfss_smart2010 ") +
  theme(plot.title = element_text(hjust = 0.5))
```

_Comment:_ The average data value of most states has a slightly decrease with fluctuation from 2002 to 2010. However, West Virginia has an obvious drop down in 2005.

c) Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

```{r 2c}
brfss_df %>%
  filter(year == "2006" | year == "2010",locationabbr == "NY") %>%
  ggplot(aes(x = response, y = data_value)) +
  geom_col() +
  facet_wrap(~year,scales = "fixed") + 
    labs(
    title = "Distribution of data value in 2006 and 2010 in NY (Overall Health)",
    x = "Response",
    y = "Data value",
    caption = "Note: Data from brfss_smart2010 ") +
  theme(plot.title = element_text(hjust = 0.5))
```

_Comment:_ For both years, response "very good" occupied most and "Poor" occupied least. Overall, there are more responses in 2010 compared to 2006.

**Problem 3**

Accelerometers have become an appealing alternative to self-report techniques for studying physical activity in observational studies and clinical trials, largely because of their relative objectivity. During observation periods, the devices measure “activity counts” in a short period; one-minute intervals are common. Because accelerometers can be worn comfortably and unobtrusively, they produce around-the-clock observations.

a) Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).

```{r 3a}
accel_df = read_csv(file = "./accel_data.csv")
accel_tidy = janitor::clean_names(accel_df) %>%
  pivot_longer(
    activity_1:activity_1440,
    names_to = "minutecount_in_24_hours",
    values_to = "activity_count",
    names_prefix = "activity_"
    ) %>% 
  mutate(
    day_tool = day,
    day_tool = recode(day, "Monday" = "1" ,"Tuesday" =  "2", "Wednesday" = "3", "Thursday" = "4", "Friday" = "5", "Saturday" = "6", "Sunday" = "7"),
    weekday = case_when(
      day_tool <= 5 ~ "weekday",
      day_tool > 5 ~ "weekend",
      TRUE ~ ""),
    minutecount_in_24_hours = as.numeric(minutecount_in_24_hours )
    ) %>% 
  select(-day_tool)
show(accel_tidy)
```

_Comment:_ accel_tidy data includes `r nrow(accel_tidy)` rows and `r ncol(accel_tidy)` columns, which is five weeks of accelerometer data collected on a 63 year-old male with BMI 25, who was admitted to the Advanced Cardiac Care Center of Columbia University Medical Center and diagnosed with congestive heart failure (CHF). 

Variables as follows:

week : which week that data was collected

day_id : which day that data was collected

day : day of the week that data was collected

minutecount_in_24_hours : the minute in the day that data was collected

activity_count :  activity counts for each minute of a 24-hour day starting at midnight

weekday: whether the day collecting data was weekday or weekend


b) Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?

```{r 3b, message = FALSE, warning = FALSE}
#create a table showing totals
total_overday = accel_tidy %>%
  group_by(week, day) %>% 
  summarize(total_of_day = sum(activity_count)) %>% 
  knitr::kable()
total_overday
```

_comment:_ Looking at the table, it is obvious that on week 4 and week 5, the activity count drops to 1440, which is 1 per minute. Besides this, there exists no apparent trend.

c) Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.

```{r 3c, warning = FALSE, message = FALSE}
accel_tidy %>% 
  ggplot(aes(x = minutecount_in_24_hours, y = activity_count, color = day)) + 
  geom_smooth(method = "loess",se = FALSE) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    title = "24-Hours Activity Count",
    x = "Time in minutes",
    y = "Activity Count",
    caption = "Data from accel_data"
  ) + 
  scale_x_continuous(
    breaks = c(0, 180, 360, 540, 720, 900, 1080, 1260, 1440), 
    labels = c("12AM", "3AM", "6AM", "9AM", "12PM", "3PM", "6PM", "9PM", "11:59PM"),
    limits = c(0, 1440)
    ) +
  theme(plot.title = element_text(hjust = 0.5))
```

_Comment:_ We could find that for most day in the week except Sunday and Tuesday, the activity count has two peak values. One is always around 9AM to 12PM and the other one is around 6PM. Lowest activity count happens in 12AM every day and ascends increasing until 9AM, fluctuates during daytime and descends after 6PM except Friday.