---
title: "p8105_hw3_js5962"
author: "Jiayao Sun"
date: '2021-10-18'
output: github_document
---

```{r 0, include = FALSE, warning = FALSE}
library(tidyverse)
library(ggridges)
library(readxl)
library(p8105.datasets)
```


**Problem 1**

```{r 1a}
data("instacart")

# How many aisles are there, and which aisles are the most items ordered from?
instacart %>%
  count(aisle) %>%
  arrange(desc(n))

```

134 aisles in total.

Then, make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.


```{r 1b}

instacart %>% 
	count(aisle) %>% 
	filter(n > 10000) %>% 
	mutate(
		aisle = factor(aisle),
		aisle = fct_reorder(aisle, n)
	) %>% 
	ggplot(aes(x = aisle, y = n)) + 
	geom_point() + 
	theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "Number of items ordered per aisle",
    x = "Aisle",
    y = "Number of items",
    caption = "limit aisles with more than 10,000 items ordered")
```

Next, make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r 1c}
instacart %>% 
	filter(
	  aisle %in% 
	    c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
	group_by(aisle) %>% 
	count(product_name) %>% 
	mutate(rank = min_rank(desc(n))) %>% 
	filter(rank <= 3) %>% 
	arrange(aisle, rank) %>% 
	knitr::kable()
```

Next, make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r 1d, message = FALSE, warning = FALSE}
instacart %>% 
	filter(
	  product_name %in% 
	    c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>%  # the day of the week on which the order was placed
  summarize(mean_hour = mean(order_hour_of_day)) %>% # the hour of the day on which the order was placed
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	) %>%
  knitr::kable()
```

***A short description of the data set***

**Problem 2**

```{r start}
data("brfss_smart2010")
```

First, do data cleaning

```{r data_clean, warning = FALSE}
brfss_df = 
  janitor::clean_names(brfss_smart2010) %>%
  filter(topic == "Overall Health") %>%
  filter(response == "Excellent" | response == "Very good" | response == "Good" | response == "Fair" | response == "Poor") %>%
  mutate(respone = as.factor(response),
  response = forcats::fct_relevel(response, c("Poor", "Fair", "Good", "Very good", "Excellent")))
```

In 2002, which states were observed at 7 or more locations? What about in 2010?

```{r 2a}
# in 2002
brfss_df %>%
  filter(year == "2002") %>%
  group_by(locationabbr) %>%
  distinct(locationdesc) %>%
  summarize(numbers_of_tested_locations = n()) %>%
  filter(numbers_of_tested_locations > 6) %>%
  arrange(numbers_of_tested_locations) %>%
  knitr::kable(caption = "Note: states observed at 7 or more location in 2002 as above.")

# in 2010
brfss_df %>%
  filter(year == "2010") %>%
  group_by(locationabbr) %>%
  distinct(locationdesc) %>%
  summarize(numbers_of_tested_locations = n()) %>%
  filter(numbers_of_tested_locations > 6) %>%
  arrange(numbers_of_tested_locations) %>%
  knitr::kable(caption = "Note: states observed at 7 or more location in 2010 as above.")
```

_Comment:_ 6 states were observed at 7 or more locations in 2002. 14 states were observed at 7 or more locations in 2010, which is larger compared to 2002.

Next, construct a data set that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r 2b}
brfss_excellent =
  brfss_df %>%
  filter(response == "Excellent") %>%
  group_by(year, locationabbr) %>%
  mutate(average_data_value = mean(data_value, na.rm = TRUE))
# create plots
brfss_excellent %>%
ggplot(aes(x = year, y = average_data_value, group = locationabbr, color = locationabbr)) + 
  geom_line() +
  geom_point(alpha = 0.3) +
  labs(
    title = "Average data value of each state in 2002-2010",
    x = "Year",
    y = "Average data value", 
    caption = "Note: Data from brfss_smart2010 ") +
  theme(plot.title = element_text(hjust = 0.5))
```

_Comment:_ The average data value of most states has a slightly decrease with fluctuation from 2002 to 2010. However, West Virginia has an obvious drop down in 2005.

Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

```{r 2c}
brfss_df %>%
  filter(year == "2006" | year == "2010",locationabbr == "NY") %>%
  ggplot(aes(x = response, y = data_value)) +
  geom_col() +
  facet_wrap(~year,scales = "fixed") + 
    labs(
    title = "Distribution of data value in 2006 and 2010 in NY (Overall Health)",
    x = "Response",
    y = "Data value",
    caption = "Note: Data from brfss_smart2010 ") +
  theme(plot.title = element_text(hjust = 0.5))
```

_Comment:_ For both years, response "very good" occupied most and "Poor" occupied least. Overall, there are more responses in 2010 compared to 2006.

**Problem 3**

Accelerometers have become an appealing alternative to self-report techniques for studying physical activity in observational studies and clinical trials, largely because of their relative objectivity. During observation periods, the devices measure “activity counts” in a short period; one-minute intervals are common. Because accelerometers can be worn comfortably and unobtrusively, they produce around-the-clock observations.
```{r}

```
